On Solving the Weighted Orthogonal Art Gallery Problem under regular grid discretization by greedy methods and their hybridizations

### 2020-10-03 doc/paper.tex
rad na tekstu

     \section{Algorithmic Approaches for WOAGP}
     \subsection{Greedy approaches for solving WOAGP}
     \subsubsection{An existing greedy method}\fxnote{TODO: Milana}
          Since the WOAGP can be seen as the Weighted Set Cover problem (WSCP) and since the best known heuristics to solve WSCP is an enhanced greedy heuristic, our idea is to transform a WOAGP instance into a WSC problem instance and then
          apply greedy algorithms to solve WOAGP. These algorithms produce a solution of reasonable quality within a short interval of time. Efficiency of such greedy heuristics is related to a greedy criterion utilized to expand current (non-complete, i.e., partial) solution to complete one. Among all candidates (solution components for expansion, that is not-yet-considered guards, we choose one with the smallest greedy value until the solution is complete (i.e., cover all  points from $D(P)$).
          A general pseudocode of Greedy heuristics is given in Algorithm~\ref{alg:greedy}

          \begin{algorithm}[!t]
          	\caption{Greedy Heuristic}\label{alg:greedy}
          	\begin{algorithmic}[1]
          		\State \textbf{Input:} an instance of a problem
          		\State \textbf{Output:} A (feasible) non-expandable solution (or reporting that no feasible solution)
          		\State $s^{P} \gets ()$ \hspace{0.3cm}// partial solution set to empty solution
          		\While{$\text{Extend}(s^{P}) \neq \emptyset$}
          		\State Select component $e \in  \text{Extend}(s^{P})$ \hspace{0.3cm}//\,w.r.t.\  some criterion
          		\State Extend $s^{P}$ by $e$
          		\EndWhile
          	\end{algorithmic}
          \end{algorithm}
    %  \subsection{Greedy Criterion based on Price-per-Unit}
      Concerning the literature for WSC problem~\ref{chvatal1979greedy, lovasz1975ratio}, one of the most efficient greedy heuristic was based on the following greedy rule:
     \begin{align}
     g(s^p, p_i) = \frac{w_{p_i}}{ f(s^p \cup \{p_i\})  - f(s^p)},
     \end{align}
     where $f(s^p) = |\bigcup_{s \in s^p} s |$.
     This heuristic is also a approximation algorithm which ensures $O(\log(n))$ approximation factor.

        \subsubsection{A Novel Greedy Heuristic}\fxnote{TODO: Dragan}
        In this subsection we present a novel greedy function, which is used in the greedy algorithm. Let us introduce a term  ``incorrect point''. For a point from $D(P)$ we say that it is incorrect if it is not covered by any guard from a current partial solution $s^{ps}$. Let denote by $incorrect_{total}$ the total number of incorrect points from discretization $D(P)$ for the current partial solution and let $w_{total}$ be the total sum of all weights among all vertices. Then, the greedy function for the given partial solution $s^{ps}$ and the guard $v$ is defined as:
        \begin{equation}\label{eq:greedyfun2}
				%$$obj(s^{ps}; v)  = \sum_{i \in s^{ps} \cup \{v\}} w_i+ incorrect_{total}$$ or
				obj(s^{ps}; v) = \frac{\sum_{i \in s^{ps} \cup \{v\}\}} w_i}{w_{total}}+ \frac{incorrect_{total}}{|D(P)|}
		\end{equation}	
            From Equation (\ref{eq:greedyfun2}) one can see that the greedy function mainly depends on the second term, since the value of the first one is not greater than 1. On other words, this function prefers such guards  which inclusion in the partial solution will cover more points. On the other side, if the inclusion of some two guards covers the same number of points, then the function suggest  the guard with lower cost. In the early stage of the greedy algorithm this approach enables that the guards which covers more points are preferable, while in a later stage, when less points remain uncovered, the function prefers the guards with lower cost.

            In the Equation.. the trade off between two terms is more balanced. In this case, the algorithm do not prefer ultimately \fxnote{TODO...}
            \begin{itemize}

@@

    \subsubsection{A hybrid of the Greedy and shaking}
    \fxnote{TODO: Ubaciti pricu o shaking $-->$ Dragan?}
    \subsubsection{A Hybrid of the Greedy + CPLEX}
        CPLEX will soon or later degrades its performance w.r.t. instance size. On the other hand, the later stage of Greedy increase the chance to worsen the final greedy solution.  So it makes sense to combine  partial solutions generated by  Greedy over a few interactions  and then to use CPLEX up to completion of the partial solution. Our approach consists of the following steps:
        \begin{enumerate}
        	\item Run a Greedy method up to $K$ iterations (parameter) to obtain a partial solution $C$ (therefore, $|C| = K$);
        	\item Take solution $C$ and make it complete via. CPLEX model.
        	\begin{itemize}
        		\item CPLEX solves corresponding sub-model which is formed by adding constraints $x_{p_i} = 1$, for all $p_i \in C$ into the existing WOAGP model;
        		\item we obtain a complete solution $C'$;
        	\end{itemize}
            \item return $f(C')$.
        \end{enumerate}

>>>>

     \section{Algorithmic Approaches for WOAGP}
     \subsection{Greedy approaches for solving WOAGP}
      Since the WOAGP can be seen as the Weighted Set Cover problem (WSCP) and since the best known heuristics to solve WSCP is an enhanced greedy heuristic, our idea is to transform a WOAGP instance into a WSC problem instance and then
          apply greedy algorithms to solve WOAGP. These algorithms produce a solution of reasonable quality within a short interval of time. Efficiency of such greedy heuristics is related to a greedy criterion utilized to expand current (non-complete, i.e., partial) solution to complete one. Among all candidates (solution components for expansion, that is not-yet-considered guards, we choose one with the smallest greedy value until the solution is complete (i.e., cover all  points from $D(P)$).
          A general pseudocode of Greedy heuristics is given in Algorithm~\ref{alg:greedy}

          \begin{algorithm}[!t]
          	\caption{Greedy Heuristic}\label{alg:greedy}
          	\begin{algorithmic}[1]
          		\State \textbf{Input:} an instance of a problem
          		\State \textbf{Output:} A (feasible) non-expandable solution (or reporting that no feasible solution)
          		\State $s^{P} \gets ()$ \hspace{0.3cm}// partial solution set to empty solution
          		\While{$\text{Extend}(s^{P}) \neq \emptyset$}
          		\State Select component $e \in  \text{Extend}(s^{P})$ \hspace{0.3cm}//\,w.r.t.\  some criterion
          		\State Extend $s^{P}$ by $e$
          		\EndWhile
          	\end{algorithmic}
          \end{algorithm}
     \subsubsection{An existing greedy method}\fxnote{TODO: Milana}

    %  \subsection{Greedy Criterion based on Price-per-Unit}
      Concerning the literature for WSC problem~\ref{chvatal1979greedy, lovasz1975ratio}, one of the most efficient greedy heuristic was based on the following greedy rule:
     \begin{align}
     g(s^p, p_i) = \frac{w_{p_i}}{ f(s^p \cup \{p_i\})  - f(s^p)},
     \end{align}
     where $f(s^p) = |\bigcup_{s \in s^p} s |$.
     This heuristic is also a approximation algorithm which ensures $O(\log(n))$ approximation factor.

        \subsubsection{A Novel Greedy Heuristic}\fxnote{TODO: Dragan}
        In this subsection we present a novel greedy function, which is used in the greedy algorithm. Let us introduce a term  ``incorrect point''. For a point from $D(P)$ we say that it is incorrect if it is not covered by any guard from a current partial solution $s^{ps}$. Let denote by $incorrect_{total}$ the total number of incorrect points from discretization $D(P)$ for the current partial solution.  Let $w_{total}$ be the total sum of all weights among all vertices and $|D(P)|$ be total number of discretization set. The greedy function for the given partial solution $s^{ps}$ and the guard $v$ takes into account both the value of the objective function of the WOAGP  applied to the partial solution if $v$ is included in it and the total number of incorrect points, given by the formula:
        \begin{equation}\label{eq:greedyfun2}
				%$$obj(s^{ps}; v)  =    \frac{\sum_{i \in s^{ps} \cup \{v\}\}} w_i}{w_{total}}+ incorrect_{total}$$ 
				g(s^{ps}; v) = \alpha \cdot \sum_{i \in s^{ps} \cup \{v\}} w_i+ \beta \cdot {incorrect_{total}}
		\end{equation}
where $\alpha$ and $\beta$ are positive real parameters.

            Although many combination of parameters $ \alpha $ and $\beta$ may be used, in our investigation we used parameter $\alpha$  only to normalize the sum of prices, i.e. $\alpha = \frac{1}{w_{total}}$ and two values for $\beta$: $\beta = 1$ and $\beta = \frac{1}{|D(P)|}$. Thus, we consider two variants of the greedy function:
                    \begin{equation}\label{eq:greedyfun3}
				g_2(s^{ps}; v)  =  \frac{\sum_{i \in s^{ps} \cup \{v\}\}} w_i}{w_{total}}+ incorrect_{total}
		\end{equation}
and 
        \begin{equation}\label{eq:greedyfun4}
				g_3(s^{ps}; v)  =    \frac{\sum_{i \in s^{ps} \cup \{v\}\}} w_i}{w_{total}}+ \frac{incorrect_{total}}{|D(P)|}
		\end{equation}
            From Equation (\ref{eq:greedyfun3}) one can see that the greedy function $g_2$ mainly depends on the second term, since the value of the first one is not greater than 1. On other words, this function prefers such guards  which inclusion in the partial solution will cover more points. On the other side, if the inclusion of some two guards covers the same number of points, then the function suggest  the guard with lower cost. In the early stage of the greedy algorithm this approach enables that the guards which covers more points are preferable, while in a later stage, when less points remain uncovered, the function prefers the guards with lower cost.

            In the Equation  (\ref{eq:greedyfun4}) the second term is also normalized and the trade off between two terms is more balanced.
            In this case, the algorithm does not  ultimately prefer any of criteria\fxnote{TODO...}
            \begin{itemize}

@@

    \subsubsection{A hybrid of the Greedy and shaking}
    \fxnote{TODO: Ubaciti pricu o shaking $-->$ Dragan?}

    \subsubsection{A Hybrid of the Greedy + CPLEX}
        CPLEX will soon or later degrades its performance w.r.t. instance size. On the other hand, the later stage of Greedy increase the chance to worsen the final greedy solution.  So it makes sense to combine  partial solutions generated by  Greedy over a few interactions  and then to use CPLEX up to completion of the partial solution. Our approach consists of the following steps:
        \begin{enumerate}
        	\item Run a Greedy method up to $K$ iterations (parameter) to obtain a partial solution $C$ (therefore, $|C| = K$);
        	\item Take solution $C$ and make it complete via. CPLEX model.
        	\begin{itemize}
        		\item CPLEX solves corresponding sub-model which is formed by adding constraints $x_{p_i} = 1$, for all $p_i \in C$ into the existing WOAGP model;
        		\item we obtain a complete solution $C'$;
        	\end{itemize}
            \item return $f(C')$.
        \end{enumerate}
